Universal Targeted Attacks for Siamese \\ Visual Tracking

### 2021-04-22 博士/论文提交/adversarial_attack/TCSVT/latex/bare_jrnl.tex
改拼写

Let $V=\{I_i\}_1^T$ denote the frames of a video sequence of length $T$. $B^{gt}=\{b^{gt}_i\}_1^T$ is used to represent the target's ground-truth position in each frame. The visual object tracking aims to predict the position $B^{pred}=\{b^{pred}_i\}_1^T$ of this target in the subsequent frames given its initial state. In SiamFC++, the tracker first transforms the paired reference frame $I_1$ and annotation $b_1^{gt}$ to get an template image $\textbf z$, and transforms the search frame $I_i$ to get the search image $\textbf x_i$ centered at the position estimated in the previous frame. At each time-step, the template image $\textbf z$ and the search image $\textbf x_i$ are first passed individually through a shared backbone network and then fused using a channel-wise correlation operation:
\begin{equation}
  f_{i}(\mathbf{z}, \mathbf{x})=\psi_{i}(\phi(\mathbf{z})) \star \psi_{i}(\phi(\mathbf{x})), i \in\{\mathrm{cls}, \mathrm{reg}\}
\end{equation}
where $\star$ denotes the channel-wise correlation operation, $\phi(\cdot)$ denotes the feature extractor of the Siamese network, $\psi_i(\cdot)$ denotes the layer specific to the classification or regression task, and $i$ denotes the specific task type ($\mathrm{cls}$ denotes the classification task and $\mathrm{reg}$ denotes the regression task). $\psi_{\mathrm{cls}}$ and $\psi_{\mathrm{reg}}$ are both designed as two convolutional layers for adapting generic features to the feature space specific to the classification/regression task. The fused features then act as input to a head network, which predicts a classification map $\textbf{C}$, a bounding box regression map $\textbf{R}$, and a quality assessment map $\textbf{Q}$ in an anchor-free manner. In short, $\textbf C$ encodes the probability of each spatial position to contain the target, $\textbf R$ regresses the bounding box of the target, and $\textbf Q$ predicts the target state estimation quality. The final bounding box is then generated according to $\textbf{C}$, $\textbf{R}$ and $\textbf{Q}$.

>>>>

Let $V=\{I_i\}_1^T$ denote the frames of a video sequence of length $T$. $B^{gt}=\{b^{gt}_i\}_1^T$ is used to represent the target's ground-truth position in each frame. The visual object tracking aims to predict the position $B^{pred}=\{b^{pred}_i\}_1^T$ of this target in the subsequent frames given its initial state. In SiamFC++, the tracker first transforms the paired reference frame $I_1$ and annotation $b_1^{gt}$ to get an template image $\textbf z$, and transforms the search frame $I_i$ to get the search image $\textbf x_i$ centered at the position estimated in the previous frame. At each time-step, the template image $\textbf z$ and the search image $\textbf x_i$ are first passed individually through a shared backbone network and then fused using a channel-wise correlation operation:
\begin{equation}
  f_{i}(\mathbf{z}, \mathbf{x})=\psi_{i}(\phi(\mathbf{z})) \star \psi_{i}(\phi(\mathbf{x})), i \in\{\mathrm{cls}, \mathrm{reg}\}
\end{equation}
where $\star$ denotes the channel-wise correlation operation, $\phi(\cdot)$ denotes the feature extractor of the Siamese network, $\psi_i(\cdot)$ denotes the layers specific to the classification or regression task, and $i$ denotes the specific task type ($\mathrm{cls}$ denotes the classification task and $\mathrm{reg}$ denotes the regression task). $\psi_{\mathrm{cls}}$ and $\psi_{\mathrm{reg}}$ are both designed as two convolutional layers for adapting generic features to the feature space specific to the classification/regression task. The fused features then act as input to a head network, which predicts a classification map $\textbf{C}$, a bounding box regression map $\textbf{R}$, and a quality assessment map $\textbf{Q}$ in an anchor-free manner. In short, $\textbf C$ encodes the probability of each spatial position to contain the target, $\textbf R$ regresses the bounding box of the target, and $\textbf Q$ predicts the target state estimation quality. The final bounding box is then generated according to $\textbf{C}$, $\textbf{R}$ and $\textbf{Q}$.
